data_cleaning_longer_period

### 2023-08-16 code/analysis_Redo.Rmd
tracking new docs

summary(as.numeric(dfc[dfc$Year == 2010,]$Total))
summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
summary(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue)

did2s(
      data = dfc %>% 
        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities) %>% 
        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Altman", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
              inner_join(dfc %>% filter(Year == 2010 & Total > 10000)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

>>>>

summary(as.numeric(dfc[dfc$Year == 2010,]$Total))
summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.67), na.rm = TRUE)

dfc.new <- dfc %>% 
        select(ID, Year, Tx, Att, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities, 
               Qcomp:Altman)

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.083) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Altman", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

event_study(data = dfc.new %>% left_join(dfc %>% select(ID, Year, Pct.NHA:Pct.COM), by = c("ID","Year")) %>% 
              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/Assets < 0.05)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

### 2023-08-16 code/data_cleaning_longer.Rmd
tracking new docs

dfc %>% 
  mutate(Liabilities = `Liabilities (as pct of assets)` * `Total net assets`, 
         Staffing = `Total expenses before depreciation` * Personnel, 
         LBE.pct = `Gross land, buildings and equipment (LBE)` / `Total net assets`, 
         `Liabilities (as pct of assets)` = `Liabilities (as pct of assets)` * 100, 
         `Surplus as a pct of before dep expenses` = `Surplus as a pct of before dep expenses` * 100, 
         Qcomp = (pap.rate + crc.rate + asthma.rate + cad.rate + ivd.rate + childbmi.rate + adultbmi.rate) / 7, 
         CostOfCare = `Total expenses before depreciation` / Total) %>%

  mutate(Liquidity =  `Total net assets` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         Profitability =  `Unrestricted surplus (deficit) before depreciation` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         Efficiency = (`Total revenue (unrestricted & restricted)` - `Total expenses before depreciation`) / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         NetWorth = (100 - `Liabilities (as pct of assets)`) / `Liabilities (as pct of assets)` / 100) %>% 
  mutate(Altmans.Z = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% # 6.56, 3.26, 6.72, 1.05  OR 0.18, 0.3, 0.81, 0.14
  mutate(Liquidity = ifelse(Liquidity == 'Inf', NA, Liquidity), 
         Profitability = ifelse(Profitability == 'Inf', NA, Profitability), 
         Efficiency = ifelse(Efficiency == 'Inf', NA, Efficiency), 
         NetWorth = ifelse(NetWorth == 'Inf', NA, NetWorth), 
         Altmans.Z = ifelse(Altmans.Z == 'Inf', NA, Altmans.Z))

@@

## Write the file
```{r}
#write_csv(dfc, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")

>>>>

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
  mutate(Att.random = ifelse(Att > 0, Att, NA))

vec.atts <- rep(c(2012:2021), (table(comp.initial$Att) / 12)[-1])

dfc <- rbind(dfc %>% filter(Att > 0), dfc %>% 
  filter(Att == 0) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att.random = sample(size = 1, vec.atts, replace = TRUE))) %>% 
  mutate(year.rel = Year - Att.random)

dfc

@@

## Write the file
```{r}
#write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
